\sys: Automated Data-Parallel Shell Processing

### 2020-04-06 pldi/draft.tex
Notes on intro

%% Title information
%% \title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
\title{DPSh: Automated Data-Parallel Processing in the Shell}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Dish}\xspace}
\newcommand{\unix}{{\scshape Unix}\xspace}

@@

\nv{I don't think the intro needs any serious rewrite, apart from deleting any
notion of distribution and highlighting parallel processing.

Key tasks, in rough order of importance:
  (i) change title and intro to avoid distribution
  (ii) cleanup and rewrite sections 4, 5: introduce our high-level figure, talk
  about things in order, add ordering in graphs, generally refine and beautify
  as much as possible.
  (iii) tighten section 2, everything in there has to be related to some part of
  the story---make the connection explicit
  (iv) Pump up evaluation: could we add 3 more micro-benchmarks? could we add
  1--2 more macro-benchmarks?
  (v) since this is IFCP, could we add some simple semantics and derivation
  rules? we should certainly be able to describe some of the optimizations as
  congruence rules.
  (vi) complete the related work with some operating-systems literature.
  --------
%   Need to highlight the use of ad-hoc flags
%   Need to highlight use cases / goals:
%     still POSIX compliant, you can replace /bin/bash with /bin/dish and see
%     \emph{some} performance improvements, even if we can't handle all cases
%     today--that is, dish enables a platform for further research.
%
%  Talk about order-aware dataflow analysis?
}

>>>>

%% Title information
%% \title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
\title{\sys: Automated Data-Parallel Shell Processing}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Pash}\xspace}
\newcommand{\unix}{{\scshape Unix}\xspace}

@@

% TODO: Important to have a small script that highlights
\nv{
(i) different classes of commands
(ii) challenge of shell expansion order
(iii) segments that are parallelized by \sys (with provable correctness)
(iv) segments that are \emph{not} parallelized by \sys (otherwise they can lead to
incorrectness)
}

% \nv{I don't think the intro needs any serious rewrite, apart from deleting any
% notion of distribution and highlighting parallel processing.
% 
% Key tasks, in rough order of importance:
%   (i) change title and intro to avoid distribution
%   (ii) cleanup and rewrite sections 4, 5: introduce our high-level figure, talk
%   about things in order, add ordering in graphs, generally refine and beautify
%   as much as possible.
%   (iii) tighten section 2, everything in there has to be related to some part of
%   the story---make the connection explicit
%   (iv) Pump up evaluation: could we add 3 more micro-benchmarks? could we add
%   1--2 more macro-benchmarks?
%   (v) since this is IFCP, could we add some simple semantics and derivation
%   rules? we should certainly be able to describe some of the optimizations as
%   congruence rules.
%   (vi) complete the related work with some operating-systems literature.
%   --------
%   Need to highlight the use of ad-hoc flags
%   Need to highlight use cases / goals:
%     still POSIX compliant, you can replace /bin/bash with /bin/dish and see
%     \emph{some} performance improvements, even if we can't handle all cases
%     today--that is, dish enables a platform for further research.
%
%  Talk about order-aware dataflow analysis?
% }
